R Notebook

### 2018-09-20 study2/study2-evid-ratio.Rmd
updated study2 modeling

>>>>

# maximum likelihood estimate with optim()

WE can do this with optim too, which will work better when we go to do it 14 times.

```{r}
inv_logit <- plogis
logit <- qlogis

evid_score_func <- function(data, par) {

  inv_logit <- plogis
  logit <- qlogis

  pred_y <- with(data,
                 {
                   inv_logit(logit(pre) + evid*par[2] + par[1])
                 }
       )
  pred_beta_A <- pred_y * par[3]
  pred_beta_B <- (1-pred_y) * par[3]

  ll <- -1 * sum(dbeta(data$post, pred_beta_A, pred_beta_B, log=TRUE)) # beta regression
  return(ll)
}

get_evid_probs <- function(result){
  # this is a heuristic/hack, could be made better but probably doesn't matter
  evid_ratio <- exp(result$par[1] + result$par[2])
  if (evid_ratio < 1) {
    p0 <- .90
  } else {
    p0 <- .50
  }

  if (p0*evid_ratio > 1) {
    p0 <- p0*.9/(p0*evid_ratio)
  }

  p1 <- p0*evid_ratio

  c(p0,p1)
}

evid_probs_to_cpt <- function(probs, var_name){
  p0 <- probs[1]
  p1 <- probs[2]

  full_list <- paste0("list(",var_name,"=c('Yes','No'), evid = c('Yes', 'No'))")
  make_custom_cpt(c(p1, p0, (1-p1), (1-p0)), c(2,2), eval(parse(text=full_list)), NULL)
}

find_evid_ratio <- function(data){
  optim(par = c(0, 0, 5), fn = evid_score_func, data = data, method="BFGS")
}

make_evid_cpt <- function(data, var_name){
  result <- find_evid_ratio(data)
  probs <- get_evid_probs(result)
  cpt <- evid_probs_to_cpt(probs, var_name)

  return(cpt)
}

evid_cpt <- make_evid_cpt(d, "diseaseSevere")

```
